\renewcommand{\bibname}{4 \hspace{.2cm} مراجع}
\begin{thebibliography}{9}
\begin{latin}
    
        \bibitem{data_compression} 
        \lr{
        Mahdi, O.A.; Mohammed, M.A.; Mohamed, A.J. (Marhc 2013)
        \textit{Implementing a Novel Approach an Convert Audio Compression to
         Text Coding via Hybrid Technique}. 
         International Journal of Computer Science Issues.  }

         \bibitem{data_types}
         \lr{
            Pujar, J.H.; Kadlaskar, L.M. (May 2010). 
            \textit{"A New Lossless Method of Image Compression and Decompression Using Huffman Coding Techniques" 
            (PDF)}. Journal of Theoretical and Applied Information Technology.
         }

         \bibitem{my_picture}
         \lr{
             Mahdi, E:
             \hyperlink{https://github.com/merfanian/DataCompressionDoc/blob/master/LatexFiles/figs/compressed.png}
             {\textit{https://github.com/\\merfanian/DataCompressionDoc/blob/master/LatexFiles/figs/compressed.png}
         }}

         \bibitem{flac}
         \lr{
             Web Archive,\hyperlink{https://web.archive.org/web/20090202063734/http://synthetic-soul.co.uk/comparison/lossless/index.asp}{\textit{
            https://web.archive.org/web/20090202063734/http://synthetic-soul.co.uk/comparison/lossless/index.asp}
         }}

         \bibitem{lossy_compression}
         \lr{
            Arcangel, Cory. (March 2013)
            \textit{ On Compression }
         }
         \bibitem{dct}
         \lr{
            Ahmed, Nasir (January 1991). 
            \textit{How I Came Up With the Discrete Cosine Transform}
         }
        %%%%%%%% Chapter 2 
         \bibitem{jpeg_example}
        \lr{
            By en:User:Cburnett - Own work in Inkscape based on the following data:, CC BY-SA 3.0, 
            \hyperlink{https://commons.wikimedia.org/w/index.php?curid=3333955}{
                \textit{https://commons.wikimedia.org/w/index.php?curid=3333955}
            }
        }

        \bibitem{youtube}
        \lr{
            Computerphile, 
            \hyperlink{https://www.youtube.com/watch?v=n\_uNPbdenRs}{
                \textit{https://www.youtube.com/watch?v=n\_uNPbdenRs}
            }
        }

        \bibitem{standard_freqs}
        \lr{
            Wikipedia, 
            \hyperlink{https://commons.wikimedia.org/wiki/File:Dctjpeg.png}{
                \textit{https://commons.wikimedia.org/wiki/File:Dctjpeg.png}
            }
        }

        \bibitem{huffman}
        \lr{
            Huffman, D. (1952). 
            \textit{"A Method for the Construction of Minimum-Redundancy Codes"}    
        }

        \bibitem{huffman_tree}
        \lr{
            Radu Trı̂mbiţaş (2012), \textit{Huffamn Codes}
        }

        \bibitem{dna}
        \lr{
          Stéphane Grumbach, FarizaTahi (November 1994), \textit{A new challenge for compression algorithms: Genetic sequences} 
        }
        
        \bibitem{uncompressed_source}
        \lr{
            Makeuseof, 
            \hyperlink{https://www.makeuseof.com/tag/audio-file-format-right-needs/}{
                \textit{https://www.makeuseof.com/tag/audio-file-format-right-needs/g}
            }
        }

        \bibitem{bitrate_definition}
        \lr{
            Gupta, Prakash C (2006). \textit{Data Communications and Computer Networks. PHI Learning.}
        }

        \bibitem{how_mp3_works}
        \lr{
            Guckert, John (Spring 2012). \textit{The Use of FFT and MDCT in MP3 Audio Compression}
        }   
        
        \bibitem{psychoacoustic}
        \lr{
            Ledgernote, \hyperlink{https://ledgernote.com/blog/q-and-a/how-does-mp3-compression-work/}{
                \textit{https://ledgernote.com/blog/q-and-a/how-does-mp3-compression-work/}
            }
        }

        \bibitem{percieved_human_hearing}
        \lr{
            Wikipedia, \hyperlink{https://commons.wikimedia.org/wiki/File:Human\_Hearing\_Graph.jpg}{
                \textit{https://commons.wikimedia.org/wiki/File:Human\_Hearing\_Graph.jpg}
            }
        }

        \bibitem{audio_masking}
        \lr{
            Wikipedia, \hyperlink{https://en.wikipedia.org/wiki/Psychoacoustics\#/media/File:Audio\_Mask\_Graph.png}{
                \textit{https://en.wikipedia.org/wiki/Psychoacoustics\#/media/File:Audio\_Mask\_Graph.png}
            }
        }
    \end{latin}
    \end{thebibliography}
    
